\documentclass[margin,line,9pt]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\usepackage{hyperref}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}

\begin{document}

\name{David P. Clark \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.5in}p{4in}}
GM.20 Maurice Keyworth Building & \\
Leeds University Business School & \\
Moorland Road  & {\it E-mail:}  \href{mailto:D.P.T.Clark@leeds.ac.uk}{D(dot)P(dot)T(dot)Clark@leeds(dot)ac(dot)uk}\\
University of Leeds   & {\it LinkedIn:} \href{http://www.linkedin.com/in/davidptclark}{www(dot)uk(dot)linkedin(dot)com/in/davidptclark}\\
Leeds, West Yorkshire & {\it Website:} \href{http://davidptclark.github.io}{davidptclark(dot)github(dot)io} \\
LS6 1AN & \\
\end{tabular}

\section{\sc Research Interests}
\begin{list2}
\item Applied microeconometrics
\item Cryptocurrencies and the dark net
\item Economics of the firm
\item Machine learning
\item Productivity analysis
\end{list2}

\section{\sc Employment}
{\bf University of Leeds}, Leeds UK\\
\vspace*{-.1in}
\begin{list1}
\item[]Teaching Fellow in Economics  \hfill {\bf September 2017 - present}
\end{list1}
\vspace*{.1in}
\section{\sc Professional Qualifications}

Fellow of the Higher Education Academy (FHEA) \hfill {\bf August 2018}

\vspace*{.1in}
\section{\sc Education}
{\bf University of Leeds}, Leeds UK\\
%{\em Department of Statistics}
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Economics  \hfill {\bf October 2013 - January 2018}
\begin{list2}
\vspace*{.05in}
\item Thesis: \textit{An Empirical Study of Firm Efficiency: New Evidence using Cross Industry and Country Data}
\item Supervisors:  Dr. Kausik Chaudhuri and Dr. Luisa Zanchi
\end{list2}
\end{list1}

\vspace*{.1in}
\begin{list1}
\item[] M.Sc. Economics: Distinction \hfill {\bf October 2012 - September 2013}
\vspace*{.05in}
\begin{list2}
\item Thesis: \textit{Corruption: Stochastic Frontier and Ordered Probit Analyses of the Firm}
\item Supervisors:  Dr. Kausik Chaudhuri and Dr. Kevin Reilly
\end{list2}
\end{list1}

\vspace*{.1in}
\begin{list1}
\item[] B.Sc.(Hons) Economics: First Class Honours \hfill {\bf September 2008 - July 2012}
\vspace*{.05in}
\begin{list2}
\item Thesis: \textit{To What Extent Does the Level of Political Independence of Central Bank Affect the Performance of Key Economic Indicators?}
\item Supervisor: Dr. Matthew Greenwood-Nimmo
\end{list2}
\end{list1}

\section{\sc Honors and Awards}
Dean's Award for Teaching Excellence\\
\vspace*{-.1in}
\begin{list2}
\item LUBS3370 Applied Econometrics \hfill{\bf 2019}
\\
\item LUBS0010 Foundation of Economics \hfill{\bf 2018}
\end{list2}

Leeds University Partnership Awards \\
\vspace*{-.1in}
\begin{list2}
\item Postgraduate Teaching Award - \textit{Shortlisted} \hfill\ {\bf 2017}
\end{list2}

Leeds University Business School Partnership Awards \hfill \\
\vspace*{-.1in}
\begin{list2}
\item Inspirational Teaching Award (shared) - \textit{Runners-up} \hfill {\bf 2020}
\item Positive Impact Award - \textit{Shortlisted} \hfill
\\
\item Personal Tutor Award - \textit{Runner-up} \hfill {\bf 2019}
\\
\item Postgraduate Teaching Award \hfill {\bf 2017}
\item Inspirational Teaching Award - \textit{Nominated}

\end{list2}

Leeds University Business School Economics Studentship \hfill {\bf 2013}

\vspace*{-2.5mm}
Humanities Scholar: for outstanding performance in first-year examinations \hfill {\bf 2009}

\vspace*{-2.5mm}
Entry to the Humanities List: for outstanding performance in first-year examinations \hfill {\bf 2009}

\section{\sc Teaching Experience}
{\bf Leeds University}, Leeds UK

\vspace{-.3cm}
{\em Workshop Assistant} \hfill {\bf May 2017}\\
Assisting with practical computer sessions across a two-day panel data econometrics workshop given by Professor Jeffery Wooldridge
entitled \href{https://lubswww.leeds.ac.uk/narti/events/article/panel-data-methodology-and-empirical-analysis-with-professor-jeffrey-m-wooldridge-registration-cl/}{"Panel Data Methodology and Empirical Analysis"}.

{\em Module Leader} \hfill {\bf February 2016  - present}\\
Duties include developing teaching materials, delivering lectures and seminars,
creating exam and coursework materials, conducting academic consultation hours and marking assessment scripts.\\

\begin{list2}
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201718&F=P&M=LUBS-3370}{LUBS3370} Applied Econometrics (jointly with Dr. Sandra Lancheros Torres)

\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201718&F=P&M=LUBS-0010}{LUBS0010} Foundations of Economics
\end{list2}

{\em Teaching Assistant} \hfill {\bf October 2014  - present}\\
Duties include leading seminars and computer lab sessions, conducting academic consultation hours and marking assessment scripts.

Graduate courses:\\
\vspace*{-.1in}
\begin{list2}
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201415&M=LUBS-5134M}{LUBS5134M} Econometrics
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201718&M=LUBS-5108M}{LUBS5108M} Applied Econometrics
\end{list2}

Undergraduate courses:\\
\vspace*{-.1in}
\begin{list2}
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201314&M=LUBS-2104}{LUBS2140} Intermediate Microeconomics
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201415&M=LUBS-2570}{LUBS2570} Introduction to Econometrics
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201415&M=LUBS-1260}{LUBS1280} Mathematical Economics
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201415&M=LUBS-1280}{LUBS1260} Mathematics for Economics and Business 1
\end{list2}

%\section{\sc Published papers}
\section{\sc Papers in preparation for submission}

Corruption, Finance and Firm Efficiency: A Stochastic Frontier Analysis Approach. \textit{(Co-authored with Kausik Chaudhuri)}

\section{\sc Working Papers}

A Comparison of Machine Learning Methods in Model Selection and Prediction: An Application to Firm-level Data

Obstacles to Firm Financing: The Role of Soft and Hard Information. \textit{(Co-authored with Kausik Chaudhuri)}

Latent Firm Obstacles and Endogeneity: An Application of the Nonparametric Instrumental Variables Estimator. \textit{(Co-authored with Kausik Chaudhuri)}

The Determinants of Obstacles to the Firm. \textit{(Co-authored with Kausik Chaudhuri)}

The Shadow Market: Asymmetric Pass-through of Real Economy Shocks to the Bitcoin Currency \textit{(Co-authored with Beulah Chelva)}

\section{\sc Conference Presentations}

\textbf{Presentations}\\
\begin{list1}
\item[] \textit{"Obstacles to Firm Financing: The Role of Soft and Hard Information"}
\vspace*{.1in}
\begin{list2}
\item Shandong University of Finance and Economics 
\item[] Cross Country Perspectives in Finance (CCPF) Conference \hfill \textbf{June 2019}
\end{list2}
\end{list1}

\vspace*{.05in}
\textbf{Poster presentations}\\
\begin{list1}
\item[] \textit{"Corruption and Firm Efficiency: A Stochastic Frontier Analysis Approach"}
\vspace*{.1in}
\begin{list2}
\item University of York, White Rose Doctoral Business and Management Conference \hfill \textbf{July 2014}
\item University of Sheffield, White Rose Doctoral Economics Conference \hfill \textbf{April 2014}
\end{list2}
\end{list1}


\section{\sc Research Experience}
{\bf Leeds University}, Leeds UK

{\em Research Assistant} \hfill {\bf May - November 2015}\\
Performing data analysis for senior research staff, aiding an ongoing research project.

\section{\sc Professional Experience}
{\bf Ernst \& Young}, Leeds UK

\vspace{-.3cm}
{\em Summer Intern} \hfill {\bf June - July 2011}\\
Based within corporate finance. Duties include working with senior analysts on accounting and restructuring of firms facing financial difficulties or ensuring potential mergers were carried out with minimal friction.

\section{\sc Computer Skills}
\begin{list1}
\item[] Statistical Packages:
	\begin{list2}
		\item Highly proficient: Eviews, R and Stata (preferred).
		\item Working knowledge: Matlab.
	\end{list2}
	\smallskip
\item[] Computing Languages:
	\begin{list2}
		\item Highly proficient: \LaTeX.
		\item Working knowledge: Bash, CSS, Git, HTML, Python and SSH.
	\end{list2}
	\smallskip
\item[] Operating Systems:  Linux, Mac OS X and Windows.\\
\end{list1}

\end{resume}
\end{document}




