\documentclass[margin,line,9pt]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
\usepackage{hyperref}

\begin{document}

\name{David P. Clark \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
4 Riverside Court& {\it E-mail:}  \href{mailto:busdptc@leeds.ac.uk}{busdptc(at)leeds(dot)ac(dot)uk}\\ 
Leeds   & {\it LinkedIn:} \href{http://www.linkedin.com/in/davidptclark}{www(dot)uk(dot)linkedin(dot)com/in/davidptclark}\\           
Leeds, West Yorkshire & {\it Website:} \href{http://davidptclark.github.io}{davidptclark(dot)github(dot)io} \\       
LS1 7BU  & \\ 
\end{tabular}


\section{\sc Research Interests}
\begin{itemize}
\item Applied microeconometrics
\item Cryptocurrencies and the digital economy
\item Economics of the firm
\item Productivity analysis	
\end{itemize}

\section{\sc Education}
{\bf University of Leeds}, Leeds UK\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Economics  \hfill {\bf October 2013 - present}
\begin{list2}
\vspace*{.05in}
\item Thesis: \textit{An Empirical Study of Firm Efficiency: New Evidence using Cross Industry and Country Data}  
\item Supervisors:  Dr. Kausik Chaudhuri and Dr. Luisa Zanchi
\end{list2}
\end{list1}

\vspace*{.1in}
\begin{list1}
\item[] M.Sc. Economics: Distinction \hfill {\bf October 2012 - September 2013}
\vspace*{.05in}
\begin{list2}
\item Thesis: \textit{Corruption: Stochastic Frontier and Ordered Probit Analyses of the Firm}
\item Supervisors:  Dr. Kausik Chaudhuri and Dr. Kevin Reilly
\end{list2}
\end{list1}

\vspace*{.1in}
\begin{list1}
\item[] B.Sc.(Hons) Economics: First Class Honours \hfill {\bf September 2008 - July 2012}
\vspace*{.05in}
\begin{list2}
\item Thesis: \textit{To What Extent Does the Level of Political Independence of Central Bank Affect the Performance of Key Economic Indicators?}
\item Supervisor: Dr Matthew Greenwood-Nimmo
\end{list2}
\end{list1}


\section{\sc Honors and Awards} 
Leeds University Partnership Awards \hfill {\bf 2017}\\
\vspace*{-.1in}
\begin{list2}
\item Postgraduate Teaching Award - Shortlisted
\end{list2}

Leeds University Business School Partnership Awards \hfill {\bf 2017}\\
\vspace*{-.1in}
\begin{list2}
\item Postgraduate Teaching Award 
\item Inspirational Teaching Award - Nominated

\end{list2}

Leeds University Business School Economics Studentship \hfill {\bf 2013}

\vspace*{-2.5mm}
Humanities Scholar: for outstanding performance in first-year examinations \hfill {\bf 2009}

\vspace*{-2.5mm}
Entry to the 'Humanities List': for outstanding performance in first-year examinations \hfill {\bf 2009}

\section{\sc Academic Experience}
{\bf Leeds University}, Leeds UK

\vspace{-.3cm}
{\em Teaching Assistant} \hfill {\bf May 2017}\\
Teaching assistant for Professor Jeffery Wooldridge, assisting with practical computer sessions across a two-day
panel data econometrics workshop. 

{\em Research Assistant} \hfill {\bf May - November 2015}\\
Performing data analysis for senior research staff aiding ongoing research projects.
\newpage
{\em Module Leader} \hfill {\bf February 2016  - present}\\
Duties include developing teaching materials, delivering lectures and seminars, 
creating exam and coursework materials, as well as marking assessment scripts.\\

\begin{list2}
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201617&F=P&M=LUBS-0010}{LUBS0010} Foundations of Economics
\end{list2}


{\em Teaching Assistant} \hfill {\bf October 2014  - present}\\
Duties include leading seminars and computer lab sessions, as well as conducting office hours.

Graduate courses:\\ 
\vspace*{-.1in}
\begin{list2}
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201415&M=LUBS-5134M}{LUBS5134M} Econometrics
\end{list2}

Undergraduate courses:\\
\vspace*{-.1in}
\begin{list2}
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201314&M=LUBS-2104}{LUBS2140} Intermediate Microeconomics 
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201415&M=LUBS-2570}{LUBS2570} Introduction to Econometrics
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201415&M=LUBS-1260}{LUBS1280} Mathematical Economics - Seminar instruction and exam marking
\item \href{http://webprod3.leeds.ac.uk/catalogue/dynmodules.asp?Y=201415&M=LUBS-1280}{LUBS1260} Mathematics for Economics and Business 1
\end{list2}

{\em Graduate Student} \hfill {\bf October 2013 - present}\\
Includes current Ph.D.~research, Ph.D.~and Masters level coursework and
research.

%\section{\sc Published papers}
\section{\sc Papers in preparation for submission}

Corruption, Finance and Firm Efficiency: A Stochastic Frontier Analysis Approach. (Co-authored with Kausik Chaudhuri)

\section{\sc Papers in progress}

Obstacles to Firm Financing: The Role of Soft and Hard Information. (Co-authored with Kausik Chaudhuri)

The Determinants of Obstacles to the Firm. (Co-authored with Kausik Chaudhuri)

The Shadow Market: Asymmetric Pass-through of Real Economy Shocks to the Bitcoin Currency (Co-authored with Beulah Chelva)
\section{\sc Conference Presentations}
\textbf{Oral Presentations}
\vspace*{.05in} 
\begin{list1}
\item[] \textit{"Corruption and Firm Efficiency: A Stochastic Frontier Analysis Approach"}
\vspace*{.1in} 
\begin{list2}
\item University of Leeds, White Rose Doctoral Economics Conference \hfill \bf{April 2015}
\end{list2}
\end{list1}

\textbf{Poster presentations}
\vspace*{.05in} 
\begin{list1}
\item[] \textit{"Corruption and Firm Efficiency: A Stochastic Frontier Analysis Approach"}
\vspace*{.1in} 
\begin{list2}
\item University of York, White Rose Doctoral Business and Management Conference \hfill \textbf{July 2014}
\item University of Sheffield, White Rose Doctoral Economics Conference \hfill \textbf{April 2014}
\end{list2}
\end{list1}


\section{\sc Professional Experience}
{\bf Ernst \& Young}, Leeds UK

\vspace{-.3cm}
{\em Summer Intern} \hfill {\bf June - July 2011}\\
Based within corporate finance. Duties include working with senior analysts on accounting and restructuring of firms facing financial difficulties or ensuring potential mergers were carried out with minimal friction.

\section{\sc Computer Skills} 
\begin{list1}
\item[] Statistical Packages:
	\begin{list2}
		\item Highly proficient: Eviews, R and Stata (preferred).	
		\item Working knowledge: Matlab.
	\end{list2}
	\smallskip
\item[] Computing Languages:
	\begin{list2}
		\item Highly proficient: \LaTeX.	
		\item Working knowledge: Bash, CSS, Git, HTML, Python and SSH.
	\end{list2}
	\smallskip
\item[] Applications: Microsoft Office Suite.
	\smallskip
\item[] Operating Systems:  Linux, Mac OS X and Windows.\\ 
\end{list1}

\begin{center}
{Last updated: \today\- •\- }
\end{center}

\end{resume}
\end{document}




